NFC and burnout in teachers - A replication and extension study

### 2022-07-25 Manuscript/Revision_Letter.Rmd
explained full model failure

@@

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

>>>>

We did start the exploratory model with the intention of using a full model, but lavaan was not able to compute it.
For transparency, we have added the intended code of the full model into our *Analyis.R* script:

> fullysat_model <- '
  # measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DRF =~ drf1 + drf2 + drf3
    DTL =~ dtl1 + dtl2 + dtl3
    MBI =~ ee + dp + rpe
    SC =~ scs
    COV =~ covb
    YST =~ years

  # structural model

    DTH ~ hnfc * NFC + hsc * SC + hcov * COV + hyst * YST
    DTL ~ lnfc * NFC + lsc * SC + lcov * COV + lyst * YST
    DRF ~ fnfc * NFC + fsc * SC + fcov * COV + fyst * YST
    MBI ~ mdth * DTH + mdtl * DTL + mdrf * DRF

    ee ~~ rpe
    ee ~~ dp
    dp ~~ rpe

    NFC ~~ YST
    NFC ~~ SC
    NFC ~~ COV
    SC ~~ COV
    SC ~~ YST
    YST ~~ COV

    DTH ~~ DTL
    DTH ~~ DRF
    DRF ~~ DTL

    dth1 ~~ dth2
    dth1 ~~ dth3
    dth2 ~~ dth3

    drf1 ~~ drf2
    drf1 ~~ drf3
    drf2 ~~ drf3

    dtl1 ~~ dtl2
    dtl1 ~~ dtl3
    dtl2 ~~ dtl3

  # Indirect effects
    Indirect1 := hnfc * mdth + hsc * mdth + hcov * mdth + hyst * mdth
    Indirect2 := lnfc * mdtl + lsc * mdtl + lcov * mdtl + lyst * mdtl
    Indirect3 := fnfc * mdrf + fsc * mdrf + fcov * mdrf + fyst * mdrf

  # contrast (if significant, the effects differ)
    Contrast := Indirect1 - Indirect2 - Indirect3

  # total effect
    Total := Indirect1 + Indirect2 + Indirect3
'
However, this code yielded multiple error messages: *lavaan* was not able to compute standard errors as the model might not be identified, it could not invert the information matrix, and estimated some latent variables with negative variances.
In short, the model could not be computed, so we used the *modindices()* function to modify it step by step, starting with the modifications with the biggest impact on model fit, but implementing only those that were contentually meaningful.
We did not document this process, which would have been a good choice in hindsight.
We adapted the explanation in the results section as follows:

> We started with a full model with all variables except for the ERQ and its subscales as they had hardly any correlations with the other variables. This model could not be computed by *lavaan*, so we modified the structure using the *modindices()*-function in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.

@@
